---
title: "Getting Started with nepExplorer"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with nepExplorer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Installation
```{r eval=FALSE}
devtools::install_github('safetyGraphics/nepExplorer', ref = 'main')
```

# Setup
```{r}
library(nepExplorer)
```

# Data Mapping
A comprehensive mapping helps nepExplorer correctly interpret your clinical trial datasets.

```{r}
custom_map <- list(
  vitals = list(
    "id_col" = "USUBJID",          # Unique subject identifier
    "treatment_col" = "ARM",        # Treatment arm
    "measure_col" = "TEST",         # Vitals measure variable
    "value_col" = "VSSTRESN",      # Vitals result value
    "unit_col" = "VSSTRESU",       # Unit of measure
    "visit_col" = "VISIT",         # Visit name
    "visitn_col" = "VISITNUM",     # Visit number
    "studyday_col" = "VSDY",       # Study day
    "vs_baseline_flag" = "ABLFL",  # Baseline flag column
    "vs_baseline_values" = list("Y" = "Y"), # Baseline value
    "measure_values" = list(
      "SYSBP" = "Systolic Blood Pressure (mmHg)",
      "DIABP" = "Diastolic Blood Pressure (mmHg)"
    )
  ),
  labs = list(
    "id_col" = "USUBJID",
    "treatment_col" = "ARM",
    "measure_col" = "LBTEST",
    "value_col" = "LBSTRESN",
    "unit_col" = "LBSTRESU",
    "studyday_col" = "LBDY",
    "visit_col" = "VISIT",
    "visitn_col" = "VISITNUM",
    "baseline_flag" = "LBBLFL",
    "baseline_values" = list("Y" = "Y"),
    "measure_values" = list(
      "ALB" = "Albumin (mg/dL)",
      "ALB/CREAT" = "Albumin/Creatinine",
      "BICARB" = "Bicarbonate (umol/L)",
      "BUN" = "Blood Urea Nitrogen (mmol/L)",
      "BUN/CREAT" = "Blood Urea Nitrogen/Creatinine",
      "CA" = "Calcium (mmol/L)",
      "CL" = "Chloride (mmol/L)",
      "CREAT" = "Creatinine (mg/dL)",
      "CYSTC" = "Cystatin C (umol/L)",
      "eGFR" = "eGFR (mL/min)",
      "eGFRcys" = "eGFRcys (mL/min)",
      "PHOS" = "Phosphate (mmol/L)",
      "K" = "Potassium (mmol/L)",
      "SODIUM" = "Sodium (mmol/L)"
    )
  ),
  dm = list(
    "id_col" = "USUBJID",
    "treatment_col" = "ARM"
  )
)
```

# Launch App
```{r eval=FALSE}
create_nepexplorer_app(
  data = list(
    dm = nepExplorer::adsl,        # Demographic data
    labs = nepExplorer::adlb,      # Laboratory measurements
    vitals = nepExplorer::advs     # Vital signs
  ),
  mapping = custom_map
)
```

# Configuration Guide

## Required Fields
- `id_col`: Unique subject identifier
- `treatment_col`: Treatment arm identifier
- `measure_col`: Measurement type column
- `value_col`: Numeric result column
- `unit_col`: Measurement units
- `visit_col`: Visit name
- `visitn_col`: Visit number
- `studyday_col`: Study day
- `baseline_flag`: Baseline identification column
- `measure_values`: Custom measurement labels

## Best Practices
- Match column names exactly to your dataset
- Modify `measure_values` to match your specific measurements
- Ensure consistent column naming across datasets

## Common Issues
- Verify data frame column names
- Check data types and formats
- Ensure all required columns are present